Formalizing the Edmonds-Karp Algorithm

### 2016-03-03 paper/root.tex
fixed listing fonts
modified diagram

\input{lstisabelle}
\lstset{captionpos=b}
\lstset{numberbychapter=false}

@@

\begin{figure}[!h]
\centering    
\begin{tikzpicture}[thick,scale=1, every node/.style={scale=1}] %change the scales if you like to reduce the size
	\begin{axis}[
		%title={Benchmark of the Edmonds-Karp algorithm},
	    axis x line*= bottom,
	    axis y line*= left,
	    xmode = log,
	    ymode = log,
	    xlabel = Number of vertices in the network,
	    ylabel = Execution time in milliseconds,
    	smooth,
	    cycle list name = black white,
	    legend style = { 
	    	at={(0.59,0.4)}, 
    	    anchor=north west,
	        draw=black, 
	        fill= white,
        	align=left
    	}
	]

>>>>

\input{lstisabelle}
\lstset{basicstyle=\small\ttfamily\slshape,breaklines=true}
\lstset{captionpos=b}
\lstset{numberbychapter=false}

@@

\begin{figure}[!h]
\centering    
\begin{tikzpicture}[thick,scale=1, every node/.style={scale=1}] %change the scales if you like to reduce the size
	\begin{axis}[
		%title={Benchmark of the Edmonds-Karp algorithm},
	    axis x line*= bottom,
	    axis y line*= left,
	    xmode = log,
	    ymode = log,
	    xlabel = Number of vertices in the network,
	    ylabel = Execution time in milliseconds,
		xticklabels={$0$, $1000$,$2000$,$3000$,$4000$},
    	smooth,
	    cycle list name = black white,
	    legend style = { 
	    	at={(0.59,0.4)}, 
    	    anchor=north west,
	        draw=black, 
	        fill= white,
        	align=left
    	}
	]
